Testing Charts: viewer's perceptual accuracy in surveys

### 2023-06-16 SDSS-2023/testing-charts-accuracy.qmd
hopefully got all of the files we want to ignore in git

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, 
                      eval = F, 
                      fig.path="./images/", 
                      fig.env="figure*", 
                      fig.align = "center",
                      dpi = 72) 
library(readr)
library(tidyverse)
library(knitr)
library(bibtex)
theme_set(theme_bw())

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, 
                      eval = F, 
                      fig.path="./images/", 
                      fig.env="figure*", 
                      fig.align = "center",
                      dpi = 72,
                      cache = TRUE) 
library(readr)
library(tidyverse)
library(knitr)
library(bibtex)
theme_set(theme_bw())
